Too good to be false: Nonsignificant results revisited

### 2016-09-20 submission/manuscript.tex
Clean repo, make sure dling files and generating ms works: YES

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle

@@

<<Dependencies, echo=FALSE, print=FALSE>>=
# Running in Sweave or running the code in Rstudio project
# If you want to run in sweave, comment out the line with run <- ''
run <- '../'
# run <- ''

# Set the cran mirror
r <- getOption("repos")
r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
options(repos = r)
# Download and load dependencies
if(!require(httr)){install.packages('httr')}
library(httr)
if(!require(latex2exp)){install.packages('latex2exp')}
library(latex2exp)
if(!require(plyr)){install.packages('plyr')}
library(plyr)
if(!require(ggplot2)){install.packages('ggplot2')}
library(ggplot2)
if(!require(stringr)){install.packages('stringr')}
library(stringr)
if(!require(car)){install.packages('car')}
library(car)
if(!require(xtable)){install.packages('xtable')}
library(xtable)

# custom functions
source(sprintf("%sfunctions/functions.R", run))
@

@@

<<Download, echo=FALSE, results=hide>>=
# Downloads the data if not available locally

# The data from the Nuijten et al paper
if(!file.exists(sprintf('%sdata/statcheck_full_anonymized.csv', run)))
{
  GET('https://osf.io/gdr4q/?action=download',
      write_disk(sprintf('%sdata/statcheck_full_anonymized.csv', run), overwrite = TRUE))
}

if(!file.exists(sprintf('%sdata/datafilegender500_post.csv', run)))
{
  # the gender related results (ALL)
  GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/datafilegender500_post.csv',
      write_disk(sprintf('%sdata/datafilegender500_post.csv', run), overwrite = TRUE))
}

if(!file.exists(sprintf('%sdata/gendercoded cleaned and discussed.csv', run)))
{
  # the coded gender results
  GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/gendercoded%20cleaned%20and%20discussed.csv',
      write_disk(sprintf('%sdata/gendercoded cleaned and discussed.csv', run), overwrite = TRUE))
}
@

<<Read in data clean data, echo=FALSE, results=hide>>=
dat <- read.csv2(sprintf("%sdata/statcheck_full_anonymized.csv", run),
                 stringsAsFactors = F,
                 dec = ",",
                 sep = ";")[-1]

# There are two test statistic indicators that are NA
# Manually correct these
dat$Statistic[is.na(dat$Statistic)] <- "F"

# Computing unadjusted and adjusted effect sizes (OBSERVED)
dat <- cbind(dat, esComp.statcheck(dat))
dat$adjESComp[dat$adjESComp < 0] <- 0

# Turning df1 for t and r into 1.
dat$df1[dat$Statistic == "t" | dat$Statistic == "r"] <- 1

# Select out incorrectly exttracted r values
dat <- dat[!(dat$Statistic=="r" & dat$Value > 1),]

# Select out irrefutably wrong df reporting
dat <- dat[!dat$df1 == 0,]

# select out NA computed p-values
dat <- dat[!is.na(dat$Computed),]

# Selecting only the t, r and F values
dat <- dat[dat$Statistic == 't' | dat$Statistic == 'r' | dat$Statistic == 'F',]
nsig <- dat$Computed >= .05
esR <- c(.1, .25, .4)
alpha = .05
alphaF = .1
@

<<Simulations, echo=FALSE, results=hide, eval = FALSE>>=
# Statistical properties of the Fisher method -----------------------------

# condition setting
N <- c(as.numeric(summary(dat$df2)[2]), # 25th percentile
       as.numeric(summary(dat$df2)[3]), # 50th percentile
       as.numeric(summary(dat$df2)[5]) # 75th percentile
)

ES <- c(.00,
        seq(.01, .99, .01))

P <- c(seq(1, 10, 1), seq(15, 50, 5))

alpha <- .05
alphaF <- 0.10
n.iter <- 10000

# NOTE: runs if the results file (N_33.csv, N_62.csv, N_119.csv) are absent

if(!file.exists(sprintf('%sdata/N_33.csv', run)) &
   !file.exists(sprintf('%sdata/N_62.csv', run)) &
   !file.exists(sprintf('%sdata/N_119.csv', run)))
{
  set.seed(35438759)
  source(sprintf('%sfunctions/simCode.R', run))
}

# Load all results back in
files <- list.files()[grepl("N_", list.files())]

names <- str_sub(files,start=1L, end=-5L)
for(i in 1:length(files)){
  assign(x = names[i], read.csv(files[i]))
  assign(x = names[i], t(get(x = names[i])[ ,-1]))
}

# Data for table
# rows are k
# columns are effect size
# N = 33
t(get(x = names[2]))
# N = 62
t(get(x = names[3]))
# N = 119
t(get(x = names[1]))

# Table 3 power computations
ser <- 1/sqrt(c(33, 62, 119)-3)
rho <- .1
zcv <- 1.282
rcv <- (exp(2*(zcv*ser))-1)/(exp(2*(zcv*ser))+1)
zrcv <- .5*log((1+rcv)/(1-rcv))
zrho <- .5*log((1+rho)/(1-rho))
round(1-pnorm(zrcv, mean=zrho, sd=ser),4)

rho <- .25
rcv <- (exp(2*(zcv*ser))-1)/(exp(2*(zcv*ser))+1)
zrcv <- .5*log((1+rcv)/(1-rcv))
zrho <- .5*log((1+rho)/(1-rho))
round(1-pnorm(zrcv, mean=zrho, sd=ser),4)

# Agresti-Coull CI
.1 - qnorm(.95, 0, 1) * (sqrt((1/10000) * .1 * .9))
.1 + qnorm(.95, 0, 1) * (sqrt((1/10000) * .1 * .9))

@

@@

The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values. However, our recalculated $p$-values assumed that all other test statistics (degrees of freedom, test values of $t$, $F$, or $r$) are correctly reported. These errors,  may have affected the results of our analyses. Since most $p$-values and corresponding test statistics were consistent in our dataset (\Sexpr{round((dim(dat)[1] - sum(dat$Error[!is.na(dat$Error)])) / dim(dat)[1] * 100,1)}\%), we do not believe these typing errors substantially affected our results and conclusions based on them.

% Sorry, inserted table manually long time ago, need to check manually
<<prep table 3, echo = FALSE, results = hide>>=
# Descriptives dataset
journals <- sort(unique(dat$journals.jour.))
for(j in 1:length(journals)){
  selJournal <- dat$journals.jour. == journals[j]
  meanK <- mean(table(dat$Source[selJournal]))
  len <- length(dat$Computed[selJournal & !is.na(dat$Computed)])
  sigRes <- sum(dat$Computed[selJournal & !is.na(dat$Computed)] < .05)
  print(
    paste0(
      journals[j], "\t", len, "\t", round(meanK, 1), "\t", sigRes, "\t", len-sigRes
    )
  )
}
@

@@

<<percentages, echo = FALSE, results = hide>>=
small <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .1) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
medium <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .1 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .25) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
large <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .25 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
larger <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100

if(!file.exists(sprintf('%sfigures/Fig1.pdf', run)))
{
  pdf(sprintf('%sfigures/Fig1.pdf', run), width=11, height=7)

  par(mai = c(1, 1, .2, .2))
  plot(density(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]),
       lty = 1,
       frame.plot = T, 
       main = "",
       xlim = c(0, 1), ylim = c(0, 2),
       xaxs = "i",
       yaxs = 'i',
       xlab = TeX("Correlation (|$\\eta$|)"),
       ylab = "Density",
       cex.axis = 1.5,
       cex.lab = 1.5,
       col = "black", las = 1, bty = 'n')
  abline(v = c(.1, .25, .4), lty = 2, col = "grey")
  t1 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .1) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
  t2 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .1 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .25) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
  t3 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .25 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
  t4 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
  text(x = .1 / 2, y = .15, labels = round(t1, 2), cex = 1)
  text(x = ((.25 - .1) / 2) + .1, y = .15, labels = round(t2, 2), cex = 1)
  text(x = ((.4 - .25) / 2) + .25, y = .15, labels = round(t3, 2), cex = 1)
  text(x = ((1 - .4) / 2) + .4, y = .15, labels = round(t4, 2), cex = 1)
  dev.off()
}

if(!file.exists(sprintf('%sfigures/Fig2.pdf', run)))
{
  pdf(sprintf('%sfigures/Fig2.pdf', run), width=11, height=7)
  par(mai = c(1, 1, .2, .2))
  # nonsignificant proportion p/year
  i <- 1
  sig <- NULL
  nsigtemp <- NULL
  kval <- NULL

  for(y in 1985:2013){
    sel <- dat$years.y. == y
    sig[i] <- sum(dat$Computed[sel] < alpha) / length(dat$Computed[sel])
    nsigtemp[i] <- sum(dat$Computed[sel] > alpha) / length(dat$Computed[sel])
    kval[i] <- median(table(dat$Source[sel])) / sum(table(dat$Source[sel]))
    i <- i + 1
  }
  par(mfrow = c(1, 1), mai = c(1, 1, .2, .2))
  plot(x = 1985:2013,
       nsigtemp,
       ylim = c(0, .4), xlim = c(1985, 2014),
       type = 'o',
       xlab = "Year", ylab = 'Proportion nonsignificant',
       yaxs = 'i', xaxt = 'n',
       cex.axis = 1.5, cex.lab = 1.5, las = 1, bty = 'n')
  axis(1, at=c(seq(1985, 2010, 5), 2013), labels = c(seq(1985, 2010, 5), 2013), col.axis="black",
       cex.axis = 1.5)
  dev.off()
}
@

Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, \Sexpr{round(small, 0)}\% were zero to small (i.e., $0\leq|\eta|<.1$), \Sexpr{round(medium, 0)}\% were small to medium (i.e., $.1\leq|\eta|<.25$), \Sexpr{round(large, 0)}\% medium to large (i.e., $.25\leq|\eta|<.4$), and \Sexpr{round(larger, 0)}\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}). This suggests that the majority of effects reported in psychology is medium or smaller (i.e., \Sexpr{round(medium+small,0)}\%), which is somewhat in line with a previous study on effect distributions \cite{Gignac2016-je}. Of the full set of 223,082 test results, 54,595 (24.5\%) were nonsiginificant, which is the dataset for our main analyses.

\begin{figure}
\begin{center}
\includegraphics{../figures/Fig1.pdf}
\end{center}
\caption{Density of observed effect sizes of results reported in eight psychology journals, with \Sexpr{round(small, 0)}\% of effects in the category none-small, \Sexpr{round(medium, 0)}\% small-medium, \Sexpr{round(large, 0)}\% medium-large, and \Sexpr{round(larger, 0)}\% beyond large.}
\label{fig:fig1}
\end{figure}

@@

<<Simulating null distribution, echo = FALSE, results = hide>>=
if(file.exists(sprintf('%sdata/simNullEs', run)))
{
  load(sprintf('%sdata/simNullEs', run))
} else
{
  # takes some time to run these, have to simulate many values
  # go get coffee
  set.seed(1234)
  simNullEs <- simNullDist(dat, n.iter = length(dat$esComp[nsig]) * 3, alpha = .05)
  simNullEs$adjESComp[simNullEs$adjESComp < 0] <- 0

  save(simNullEs, file = sprintf('%sdata/simNullEs', run))
}

temp <- ks.test(simNullEs$esComp,
                dat$esComp[nsig],
                alternative="greater")

if(!file.exists(sprintf('%sfigures/Fig3.pdf', run)))
{
  pdf(sprintf('%sfigures/Fig3.pdf', run), width=11, height=7)
  par(mfrow = c(1,2), mai = c(1.2,1.2,.8,.5))
  # Overall
  plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
       lty = 1,
       frame.plot = T, 
       main = TeX(
         sprintf(
           "Unadjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
       xlim = c(0, 1),
       xaxs = "i",
       yaxs = "i",
       xlab = TeX("Correlation (|$\\eta$|)"),
       ylab = "Cumulative density",
       cex.axis=.8,
       cex.lab=1,
       cex.main=1.5,
       col = "grey", las=1)
  lines(ecdf(na.omit(sqrt(dat$esComp[nsig]))))
  legend(x = .6, y = .2, legend = c(TeX("$H_0$"), 'Observed'),
         cex = 1, lty = c(1, 1),
         col = c("grey", "black", 2),
         box.lwd = 0, lwd = 2, bty = 'n')
  for(es in esR){
    h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
    clip(es, 1, 0, h0horiz)
    abline(h = h0horiz, v = es, lty = 2, col = "grey")
    clip(0, 1, 0, 1)
    text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
    x <- sqrt(dat$esComp[nsig]) <= es
    horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
    text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
    clip(0, es, 0, horiz)
    abline(h = horiz, v = es, lty = 2, col = "black")
    clip(0, 1, 0, 1)
  }
}

temp <- ks.test(simNullEs$adjESComp,
                dat$adjESComp[nsig],
                alternative="greater")
# Overall[adj]
plot(ecdf(na.omit(sqrt(simNullEs$adjESComp))),
     lty = 1,
     frame.plot = T, 
     main = TeX(
       sprintf(
         "Adjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
     xlim = c(0, 1),
     xaxs = "i",
     yaxs = "i",
     xlab = TeX("Correlation (|$\\eta$|)"),
     ylab = "Cumulative density",
     cex.axis = .8,
     cex.lab = 1,
     cex.main = 1.5,
     col = "grey", las = 1)
lines(ecdf(na.omit(sqrt(dat$adjESComp[nsig]))))
legend(x = .6,y = .2,legend = c(TeX("$H_0$"), 'Observed'),
       cex = 1,lty = c(1, 1),
       col = c("grey", "black", 2), box.lwd = 0, lwd = 2, bty = 'n')
for(es in esR){
  h0horiz <- sum(sqrt(simNullEs$adjESComp[!is.na(simNullEs$adjESComp)]) < es) / length(simNullEs$adjESComp[!is.na(simNullEs$adjESComp)])
  clip(es, 1, 0, h0horiz)
  abline(h = h0horiz, v = es, lty = 2, col = "grey")
  clip(0, 1, 0, 1)
  text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
  x <- sqrt(dat$adjESComp[nsig]) <= es
  horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
  text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
  clip(0, es, 0, horiz)
  abline(h = horiz, v = es, col = "black", lty = 2)
  clip(0, 1, 0, 1)
}
dev.off()

if(!file.exists(sprintf('%sfigures/S1Fig.pdf', run)))
{
  pdf(sprintf('%sfigures/S1Fig.pdf', run), onefile = TRUE, width = 11, height = 11)
  par(mfrow = c(2, 2), mai = c(1.2, 1.2, .8, .5))

  for(i in 1:4){
    sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
    set.seed(i)
    simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha = .05)
    temp <- ks.test(simNullEs$esComp,
                    dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
                    alternative = "greater")
    print((temp))
    if(i == 3){
      plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
           lty = 1,
           frame.plot = T, 
           main = TeX(
             sprintf("%s, D=%s, $p=7.934\\times 10^{-6}$",
                     sort(unique(dat$journals.jour.))[i],
                     round(temp$statistic,3))),
           xlim = c(0,1),
           xaxs = "i",
           yaxs = "i",
           xlab = TeX("Correlation (|$\\eta$|)"),
           ylab = "Cumulative density",
           cex.axis = .8,
           cex.lab = 1,
           cex.main = 1.5,
           col = "grey", las = 1)
    }
    else{plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
              lty = 1,
              frame.plot = T, 
              main = TeX(
                sprintf("%s, D=%s, $p=2.2\\times 10^{-16}$",
                        sort(unique(dat$journals.jour.))[i],
                        round(temp$statistic,3))),
              xlim = c(0,1),
              xaxs = "i",
              yaxs = "i",
              xlab = TeX("Correlation (|$\\eta$|)"),
              ylab = "Cumulative density",
              cex.axis = .8,
              cex.lab = 1,
              cex.main = 1.5,
              col = "grey", las = 1)}
    lines(ecdf(sqrt(dat$esComp[sel])),
          lwd = .5)
    legend(x = .6, y = .2, legend = c(TeX("$H_0$"), 'Observed'),
           cex = 1.2, lty = c(1, 1),
           col = c("grey", "black", 2), box.lwd = 0, lwd = 2, bty = 'n')
    for(es in esR){
      h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
      clip(es, 1, 0, h0horiz)
      abline(h = h0horiz, v = es, lty = 2, col = "grey")
      clip(0, 1, 0, 1)
      x <- sqrt(dat$esComp[sel]) <= es
      horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
      text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1.2)
      text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1.2, col = 'darkgrey')
      clip(0, es, 0, horiz)
      abline(h = horiz, v = es, col = "black", lty = 2)
      clip(0, 1, 0, 1)
    }
  }

  for(i in 5:8){
    sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
    set.seed(i)
    simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha=.05)
    temp <- ks.test(simNullEs$esComp,
                    dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
                    alternative="greater")
    print((temp))
    plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
         lty = 1,
         frame.plot = T, 
         main = TeX(
           sprintf("%s, D=%s, $p=2.2\\times 10^{-16}$",
                   sort(unique(dat$journals.jour.))[i],
                   round(temp$statistic,3))),
         xlim = c(0, 1),
         xaxs = "i",
         yaxs = "i",
         xlab = TeX("Correlation (|$\\eta$|)"),
         ylab = "Cumulative density",
         cex.axis = .8,
         cex.lab = 1,
         cex.main = 1.5,
         col = "grey", las = 1)
    lines(ecdf(sqrt(dat$esComp[sel])),
          lwd = .5)
    legend(x = .6,y = .2,legend = c(TeX("$H_0$"), 'Observed'),
           cex = 1.2,lty = c(1, 1),
           col = c("grey", "black", 2), box.lwd = 0 , lwd = 2, bty = 'n')
    for(es in esR){
      h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
      clip(es, 1, 0, h0horiz)
      abline(h = h0horiz, v = es, lty = 2, col = "grey")
      clip(0, 1, 0, 1)
      x <- sqrt(dat$esComp[sel]) <= es
      horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
      text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1.2)
      text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1.2, col = 'darkgrey')
      clip(0, es, 0, horiz)
      abline(h = horiz, v = es, col = "black", lty = 2)
      clip(0, 1, 0, 1)
    }
  }
  dev.off()
}

@

For the entire set of nonsignificant results across journals, Figure \ref{fig:fig3} indicates that there is substantial evidence of false negatives. Under $H_0$, 46\% of all observed effects is expected to be within the range $0\leq|\eta|<.1$, as can be seen in the left panel of Figure \ref{fig:fig3} highlighted by the lowest grey line. However, of the observed effects, only 26\% fall within this range, as highlighted by the lowest black line. Similarly, we would expect 85\% of all effect sizes to be within the range $0\leq|\eta|<.25$ (middle grey line), but we observed 14 percentage points less in this range (i.e., 71\%; middle black line); 96\% is expected for the range $0\leq|\eta|<.4$ (top grey line), but we observed 4 percentage points less (i.e., 92\%; top black line). These differences indicate that larger nonsignificant effects are reported in papers than expected under a null effect. This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=\Sexpr{round(temp$statistic, 2)}$, $p<.000000000000001$. Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see \href{../figures/S1Fig}{Figure S1} for results per journal).

@@

<<Paper level application, echo = FALSE, results = hide>>=
# Computing the Fisher Tests
if(!file.exists(sprintf('%sdata/fishRes', run)))
{
  fishRes <- FisherMethod(dat$Computed, as.character(dat$Source))
  save(fishRes, file = sprintf('%sdata/fishRes', run))
} else
{
  load(sprintf('%sdata/fishRes', run))
}

if(!file.exists(sprintf('%sdata/fishDF', run)))
{
  # Get vector to identify which papers are from which journal
  sourcejour <- NULL
  for(i in 1:length(unique(dat$Source))){
    sourcejour[i] <- unique(dat$journals.jour.[dat$Source==unique(dat$Source)[i]])
  }

  years <- NULL
  for(i in 1:length(sort(unique(dat$Source)))){
    sel <- dat$Source == sort(unique(dat$Source))[i]
    years[i] <- unique(dat$years.y.[sel])
    print(i)
  }

  # Make vector of sig/nsig/na 
  fishDF <- data.frame(FisherP=fishRes$PFish, journal=sourcejour, kRes=fishRes$CountNSig, year=years)

  save(fishDF, file = sprintf('%sdata/fishDF', run))
} else
{
  load(sprintf('%sdata/fishDF', run))
}

alphaF <- 0.10
# Compute amount of papers and proportion of sig/nsig/NA Fisher Method tests
final <- NULL
kLen <- c(1, 2, 3, 4, 5, 10, 20)

for(journals in sort(unique(dat$journals.jour.))){
  sel <- fishDF$journal == journals

  # Amount of papers in a journal
  amount <- length(fishDF$FisherP[sel])
  # Proportion of significant fisher results
  amountSig <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP)] < alphaF)

  # Amount of papers in a journal without significant results
  countNA <- sum(is.na(fishDF$FisherP[sel]))
  journalSet <- NULL  
  # Writing out the results
  for(k in 1:length(kLen)){
    if(k == 7){
      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes >= kLen[k]] < alphaF) / length(fishDF$FisherP[sel  & fishDF$kRes >= kLen[k]])
      journalSet <- cbind(journalSet, x)
    }
    else if(k == 5 | k ==6){
      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes >= kLen[k]& fishDF$kRes < kLen[k+1]] < alphaF) / length(fishDF$FisherP[sel & fishDF$kRes >= kLen[k]& fishDF$kRes < kLen[k+1]])
      journalSet <- cbind(journalSet, x)
    } else{
      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes == kLen[k]] < alphaF) / length(fishDF$FisherP[sel & fishDF$kRes == kLen[k]])
      journalSet <- cbind(journalSet, x)}
  }
  temp <- cbind(journals,
                journalSet,
                amountSig / amount,
                countNA,
                amountSig,
                amount)
  # This is the result that goes into the table
  final <- rbind(final, temp)
}
temp <- "Overall"
for(i in 1:length(kLen)){
  if(i == 7){
    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes >= kLen[i] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes >= kLen[i]])
  }
  else if(i == 5|i == 6){
    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes >= kLen[i] &fishDF$kRes < kLen[i+1] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes >= kLen[i] & fishDF$kRes < kLen[i+1]])
  }
  else{
    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes == kLen[i] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes == kLen[i]])  
  }

}
temp <- c(temp,
          sum(as.numeric(as.character(final[,dim(final)[2]-1])))/sum(as.numeric(as.character(final[,dim(final)[2]]))),
          sum(as.numeric(as.character(final[,dim(final)[2]-2]))),
          sum(as.numeric(as.character(final[,dim(final)[2]-1]))),
          sum(as.numeric(as.character(final[,dim(final)[2]]))))
final <- rbind(as.character(temp), final)
final <- as.data.frame(final)

names(final) <- c('journals', paste0('k', kLen), 'overall', 'countNA', 'amountSig', 'nrpapers')
# write.csv(final, 'table4.csv', row.names=F)

# Overall
table(fishDF$kRes)
# Per journal
table(fishDF$kRes[fishDF$journal=="DP"])
table(fishDF$kRes[fishDF$journal=="FP"])
table(fishDF$kRes[fishDF$journal=="JAP"])
table(fishDF$kRes[fishDF$journal=="JCCP"])
table(fishDF$kRes[fishDF$journal=="JEPG"])
table(fishDF$kRes[fishDF$journal=="JPSP"])
table(fishDF$kRes[fishDF$journal=="PLOS"])
table(fishDF$kRes[fishDF$journal=="PS"])

# Median per journal
x = as.numeric(as.character(final$amountSig)) / (as.numeric(as.character(final$nrpapers)) - as.numeric(as.character(final$countNA)))
y = c(median(fishDF$kRes[fishDF$journal=="DP"]),
      median(fishDF$kRes[fishDF$journal=="FP"]),
      median(fishDF$kRes[fishDF$journal=="JAP"]),
      median(fishDF$kRes[fishDF$journal=="JCCP"]),
      median(fishDF$kRes[fishDF$journal=="JEPG"]),
      median(fishDF$kRes[fishDF$journal=="JPSP"]),
      median(fishDF$kRes[fishDF$journal=="PLOS"]),
      median(fishDF$kRes[fishDF$journal=="PS"]))
cor(x[-1], y)

# Computing the number of significant Fisher results per year
# As proportion of all papers reporting nonsignificant results
fishDF$logicalP <- ifelse(fishDF$FisherP < .1, 1, 0)
fisherYear <- ddply(fishDF, .(year), summarise, propYear=mean(logicalP, na.rm=TRUE))

knsYear <- ddply(fishDF, .(year), summarise, kYear=mean(kRes, na.rm=TRUE))
pmeanYear <- ddply(dat[dat$Reported.Comparison == '=' & dat$Reported.P.Value > .05, ],
                   .(years.y.), summarise, pYear=mean(Reported.P.Value, na.rm=TRUE))

esYear <- ddply(dat[dat$Reported.Comparison == '=' & dat$Reported.P.Value > .05, ],
                .(years.y.), summarise, esYear=mean(esComp, na.rm=TRUE))

mydf <- data.frame(x = fisherYear$year,
                   y = fisherYear$propYear,
                   count = knsYear$kYear)

mydf

if(!file.exists(sprintf('%sfigures/Fig4.pdf', run)))
{
  ggplot(mydf, aes(x = x, y = y)) + geom_point(aes(size = count)) + ylim(0, 1) + geom_smooth(method="lm") +
    xlab("Year") + ylab("Proportion significant Fisher results")

  ggsave(filename = sprintf('%sfigures/Fig4.pdf', run), plot = last_plot(), width = 7, height = 5)
}

# sample size development over time
medianN <- NULL
p25 <- NULL
p75 <- NULL
i <- 1
for(y in 1985:2013){
  temp <- summary(dat$df2[dat$years.y. == y])

  medianN[i] <- temp[3]
  p25[i] <- temp[2]
  p75[i] <- temp[5]

  i <- i + 1
}

if(!file.exists(sprintf('%sfigures/Fig5.pdf', run)))
{
  pdf(sprintf('%sfigures/Fig5.pdf', run), width=7, height=6)
  par(mar = c(4, 4, .2, 2))
  plot(x=1985:2013, y=medianN, type='o', col="black",
       ylab="Degrees of freedom", xlab="Year",
       xlim = c(1985, 2015), 
       ylim=c(0,150), cex.lab=1.2, las=1, lwd=1, cex.axis=1.2, xaxs='i',
       yaxs='i',
       bty = 'n')
  lines(x=1985:2013, y=p25, type='o', col='grey')
  lines(x=1985:2013, y=p75, type='o', col='grey')
  text(y = 100, x = 2010, "P75", col = "grey")
  text(y = 50, x = 2010, "P50", col = "black")
  text(y = 22, x = 2010, "P25", col = "grey")
  dev.off()
}
@

@@

<<gender, echo = FALSE, results = hide>>=
# 27,523 gender results
# manually extracted from datafilegender500_post.csv
# number of rows (take into account header row)

# gender effect evaluated -------------------------------------------------

gend <- read.csv2(sprintf('%sdata/gendercoded cleaned and discussed.csv', run), sep = ";", dec = ".", header = TRUE)

# 1 = null expected
# 2 = effect expected
# 3 = no expectation
table(gend$significance, gend$final_code)

options(scipen = 5, digits = 8)
# sel <- gend$significance == "significant" & gend$final_code == "no expectation"
for(sig in unique(gend$significance)){
  for(code in unique(gend$final_code[!is.na(gend$final_code)])){
    sel <- gend$significance == sig & gend$final_code == code

    if(sig == "significant"){
      temp <- gend$Computed[sel] / .05
      pstar <- temp[!is.na(temp)]
      x$CountNSig <- length(pstar)
      x$Fish <- -2*sum(log(pstar))
      x$PFish <- pchisq(x$Fish, df = 2 * length(pstar), lower.tail = FALSE)
    }
    if(sig == "nonsignificant"){
      x <- (FisherMethod(x = gend$Computed[sel], id = 1, alpha = 0.05))
    }

>>>>

\usepackage{Sweave}
\begin{document}
\input{manuscript-concordance}
\maketitle

@@

@@

@@

The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values. However, our recalculated $p$-values assumed that all other test statistics (degrees of freedom, test values of $t$, $F$, or $r$) are correctly reported. These errors,  may have affected the results of our analyses. Since most $p$-values and corresponding test statistics were consistent in our dataset (90.7\%), we do not believe these typing errors substantially affected our results and conclusions based on them.

% Sorry, inserted table manually long time ago, need to check manually

@@

Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, 7\% were zero to small (i.e., $0\leq|\eta|<.1$), 23\% were small to medium (i.e., $.1\leq|\eta|<.25$), 27\% medium to large (i.e., $.25\leq|\eta|<.4$), and 42\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}). This suggests that the majority of effects reported in psychology is medium or smaller (i.e., 30\%), which is somewhat in line with a previous study on effect distributions \cite{Gignac2016-je}. Of the full set of 223,082 test results, 54,595 (24.5\%) were nonsiginificant, which is the dataset for our main analyses.

\begin{figure}
\begin{center}
\includegraphics{../figures/Fig1.pdf}
\end{center}
\caption{Density of observed effect sizes of results reported in eight psychology journals, with 7\% of effects in the category none-small, 23\% small-medium, 27\% medium-large, and 42\% beyond large.}
\label{fig:fig1}
\end{figure}

@@

For the entire set of nonsignificant results across journals, Figure \ref{fig:fig3} indicates that there is substantial evidence of false negatives. Under $H_0$, 46\% of all observed effects is expected to be within the range $0\leq|\eta|<.1$, as can be seen in the left panel of Figure \ref{fig:fig3} highlighted by the lowest grey line. However, of the observed effects, only 26\% fall within this range, as highlighted by the lowest black line. Similarly, we would expect 85\% of all effect sizes to be within the range $0\leq|\eta|<.25$ (middle grey line), but we observed 14 percentage points less in this range (i.e., 71\%; middle black line); 96\% is expected for the range $0\leq|\eta|<.4$ (top grey line), but we observed 4 percentage points less (i.e., 92\%; top black line). These differences indicate that larger nonsignificant effects are reported in papers than expected under a null effect. This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=0.25$, $p<.000000000000001$. Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see \href{../figures/S1Fig}{Figure S1} for results per journal).

@@

@@
